BOAST: a Metaprogramming Framework to Produce Portable and Efficient Computing Kernels for HPC Applications

### 2014-07-15 Paper/BOAST.tex
update paper with JF remarks

Généricité
 et
fonctionalités

@@

The race to exascale is not going to simplify the environment. All of the
above architectures can be considered. For instance European FP7 project Deep
considers using Accelerators (XEON Phi) while the European FP7 project
Mont-Blanc considers using low-power embedded processor with integrated
GPU. Network architectures are also part of the architecture and can be
very diverse.

transition architecture application

@@

Ajouter Multiplicité des devs et donc problèmatique de maintenabilité ++

In Section~\ref{use_cases} we will present two HPC application that we used
as use cases: SPECFEM3D and BigDFT. They are both based on computing
kernels.

  \subsection{Performance Portability of Computing Kernels}

@@

>>>>

Genericity of HPC codes is often limited. Producing generic code in FORTRAN
90/95 is difficult as the language is not really  fit for it.

Functionality of HPC codes is tied to the previous point. Without genericity,
adding new functionalities can be quite costly.

@@

The race to exascale is not going to simplify the environment. All of the above
architectures can be considered. Network architectures are also part of the
architecture and can be very diverse.  For instance European FP7 project DEEP
considers using Accelerators (XEON Phi) while the European FP7 project
Mont-Blanc considers using low-power embedded processor with integrated GPU.

Running axisting applications on those new architectures is an open project.
Thus, those projects have work packages dedicated to applications. Those
workpackages are dedicated to porting and optimizing Scientific applications on
those new architectures. In the DEEP project six applications were selected for
porting and optimizing, eleven were selected in the Mont-Blanc project.

@@

Those applications are often developed by several individuals. Sometimes some of
those developers only work a few month on the application. Maintaining optimized
code written by someone else is quite a challenge.

In Section~\ref{use_cases} we will present two HPC application that we used
as use cases: SPECFEM3D and BigDFT. They are both based on computing
kernels and were selected as candidate applications in the Mont-Blanc project.

  \subsection{How Should Computing Kernels be Written?}

@@

What we want is computing kernels that are:
\begin{itemize}
\item Written in a portable manner,
\item Written in a way that raise developer productivity,
\item Written to present good performance.
\end{itemize}
